Transactional Memory Concurrency Verification with Landslide

### 2018-03-13 htm/paper.tex
cuidado!

\begin{lemma}[Equivalence of Aborts]
	\label{lem:equiv}
	Let:%
	\footnote{Arbitrary code may not be structured to distinguish these as nicely as in our examples;
	e.g., more code may exist in the success branch after {\tt \_xend()};
	such would be considered part of $\omega$ here.}
	\begin{itemize}
		\item $\tiiat{\alpha}$ be an HTM begin operation,
		\item $\tiiat{\beta_1}\dots\tiiat{\beta_n}$ be the transaction body (with $\beta_n$ the HTM end call),
		\item $\tiiat{\phi_1}\dots\tiiat{\phi_m}$ be the failure path, and
		\item $\tiiat{\omega_1}\dots\tiiat{\omega_l}$ be the subsequent code executed unconditionally.
	\end{itemize}
	Then, for any interleaving prefix%
	\footnote{Without loss of generality: for any number of other threads \tjj/\tkk,
	and for any number of thread switches away from \tii during the transaction.}
	\[
	\begin{tabular}{c}
		$\tiiat{\alpha},\tiiat{\beta_1}\dots\tiiat{\beta_b},$\\
		$\tjjat{\gamma_1}\dots\tjjat{\gamma_j},$ \\
		$\tkkat{\kappa_1}\dots\tkkat{\kappa_k},$ \\
		$\tiiat{\beta_{b+1}}$ % $\dots\tiiat{\beta_{n-1}}$ -- excluded bc might abort
	\end{tabular}
	\]
	with $b<n$, $j \ne i$, $k \ne i$, etc., either:
	\begin{enumerate}
		\item $\tiiat{\alpha},\tjjat{\gamma_1}\dots\tjjat{\gamma_j},\tkkat{\kappa_1}\dots\tkkat{\kappa_k},\tiiat{\phi_1}\dots$
			(conflicting case), or
		\item $\tiiat{\alpha},\tiiat{\beta_1}\dots\tiiat{\beta_b}\dots\tiiat{\beta_n},\tjjat{\gamma_1}\dots\tjjat{\gamma_j},$ \\
			$\tkkat{\kappa_1}\dots\tkkat{\kappa_k}$
			(independent case)
	\end{enumerate}
	is observationally equivalent.
\end{lemma}

@@

\begin{itemize}
	\item {\bf Limited Happens-Before.}
	\item {\bf Pure Happens-Before.}
\end{itemize}

>>>>

\newcommand\llama[1]{\includegraphics[width=#1]{llama.pdf}}
\newcommand\llitem{\item[\raisebox{-0.15em}{\llama{1.2em}}]}

\begin{lemma}[Equivalence of Aborts]
	\label{lem:equiv}
	Let:%
	\footnote{Arbitrary code may not be structured to distinguish these as nicely as in our examples;
	e.g., more code may exist in the success branch after {\tt \_xend()};
	such would be considered part of $\omega$ here.}
	\begin{itemize}
		\llitem $\tiiat{\alpha}$ be an HTM begin operation,
		\llitem $\tiiat{\beta_1}\dots\tiiat{\beta_n}$ be the transaction body (with $\beta_n$ the HTM end call),
		\llitem $\tiiat{\phi_1}\dots\tiiat{\phi_m}$ be the failure path, and
		\llitem $\tiiat{\omega_1}\dots\tiiat{\omega_l}$ be the subsequent code executed unconditionally.
	\end{itemize}
	Then, for any interleaving prefix%
	\footnote{Without loss of generality: for any number of other threads \tjj/\tkk,
	and for any number of thread switches away from \tii during the transaction.}
	\[
	\begin{tabular}{c}
		$\tiiat{\alpha},\tiiat{\beta_1}\dots\tiiat{\beta_b},$\\
		$\tjjat{\gamma_1}\dots\tjjat{\gamma_j},$ \\
		$\tkkat{\kappa_1}\dots\tkkat{\kappa_k},$ \\
		$\tiiat{\beta_{b+1}}$ % $\dots\tiiat{\beta_{n-1}}$ -- excluded bc might abort
	\end{tabular}
	\]
	with $b<n$, $j \ne i$, $k \ne i$, etc., either:
	\begin{enumerate}
		\item $\tiiat{\alpha},\tjjat{\gamma_1}\dots\tjjat{\gamma_j},\tkkat{\kappa_1}\dots\tkkat{\kappa_k},\tiiat{\phi_1}\dots$
			(conflicting case), or
		\item $\tiiat{\alpha},\tiiat{\beta_1}\dots\tiiat{\beta_b}\dots\tiiat{\beta_n},\tjjat{\gamma_1}\dots\tjjat{\gamma_j},$ \\
			$\tkkat{\kappa_1}\dots\tkkat{\kappa_k}$
			(independent case)
	\end{enumerate}
	is observationally equivalent.
\end{lemma}

@@

\begin{itemize}
	\llitem {\bf Limited Happens-Before.}
	\llitem {\bf Pure Happens-Before.}
\end{itemize}
